Pilot data analysis

### 2020-12-07 pilot_data_analysis.Rmd
Remove test data files

participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")
paste0(participant_list_for_prolific, sep = "\n") %>% writeClipboard() # works on windows

>>>>

#participants_to_exclude[,1:3]

participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")

paste0(participant_list_for_prolific, sep = "\n") %>% writeClipboard() # works on windows

exclude_list_for_prolific <- str_extract(string = participants_to_exclude$source, pattern = "[a-z0-9]{24}") %>% paste0(collapse = "\n")
